Idealized Wind Models of Cool Gas Outflows

### 2010-08-17 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5133 ac11df5e-a788-c23b-a8e1-c758c323924d

\newcommand{\tpk}{$\tau_{\rm pk}$}
\newcommand{\mtpk}{\tau_{\rm pk}}
\newcommand{\mdv}{\delta v}
\newcommand{\ewabs}{$W_{\rm a}$}
\newcommand{\ewe}{$W_{\rm e}$}
\newcommand{\rtt}{$r_{\tau = 0.2}$}
\newcommand{\mrtt}{r_{\tau = 0.2}}
\newcommand{\bturb}{$b_{\rm turb}$}
\newcommand{\mbturb}{b_{\rm turb}}
\newcommand{\taud}{$\tau_{\rm dust}$}
\newcommand{\mtaud}{\tau_{\rm dust}}
\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\feiis}{\ion{Fe}{2}$*$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {\, {\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

Beyond $z \sim 0$, galactic outflows are 
revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
\ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
as a backlight, one observes gas that is predominantly
blue-shifted which indicates a flow toward
Earth and away from the galaxy.  These transitions are sensitive to
the cool (\ion{Mg}{2}; $T \sim 10^4$K) and warm (\ion{C}{4}; $T \sim
10^5$K) phases of the flow.  The incidence of cool gas outflows is
nearly universal in star-forming galaxies;  this includes systems at $z \sim 0$
which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
\citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin09}, and
$z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97,shapley03}.

@@

Recent studies of $z \sim 1$ star-forming galaxies have revealed that
the cool gas often exhibits significant resonant-line emission (e.g.\
\ion{Mg}{2}) in
tandem with the nearly ubiquitous blue-shifted absorption
\citep{wcp+09,rubin09,rubin+10b}.  The resultant spectra resemble the P-Cygni
profile characteristic of stellar winds.
\cite{rubin+10a} have also detected line
emission from non-resonant \ion{Fe}{2}$^*$ transitions 
Their interpretation is that the emission is the result of photons
scattered off the wind into our sightline, analogous to P-Cygni.
\cite{rubin+10a} also observed spatially extended \ion{Mg}{2} emission
which they use to estimate the size of the outflow.  They infer that
the wind extends to at least 5\,kpc from the galaxy.  Line emission is
also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
A comprehensive analysis of the emission lines
related to galactic-scale outflows
(e.g.\ via deep integral-field-unit observations) may offer unique
diagnostics on the morphology and density of the outflow, eventually
setting tighter constraints on the energetics of the flow.

[Phillips first reported?]
Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
and \cite{rubin+10c}.   
\cite{wcp+09}, who
studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
\ion{Mg}{2} emission in a small subset of the individual galaxy
spectra of their large sample.  These were excluded from the full
analysis on concerns that the emission was related to AGN activity.
The stacked spectra of the remaining galaxies, however, also indicated
\ion{Mg}{2} emisison, both directly and when the authors modeled and
`removed' the $v \approx 0\mkms$ absorption component.  Although the
authors suggested the emission could be related to back-scattered
light in the wind, they also allowed that it could be related to weak
AGN activity.   Very similar \ion{Mg}{2} emission was observed by
\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
of lower redshift galaxies. 
[Did Kate see FeII* emission in her stacks? If not, why not?]

@@

Focusing further on the \ion{Mg}{2} absorption, one notes that the profiles lie
well above zero intensity and have similar depth even though their $f\lambda$
values differ by a factor of two.  In standard absorption line
analysis, this is 
the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
saturated) which only partially covers the emitting source
\citep[e.g.][]{hamann+10}.  Our fiducial wind model, however, 
{\it entirely covers the source}; the apparent partial covering must
be related to a different effect.
Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
absorption profiles from Figure~\ref{fig:fiducial_1d} against an
artificial model where no absorbed photons are 
re-emitted.   As expected from the
$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), this
`intrinsic' model
produces a strong \mgiid\ doublet that absorbs all photons at
$\delta v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
  max}_{2796}) \approx 0$.
The true model, in contrast, has been `filled in' at $\delta v \approx -100
\mkms$ by photons scattered in the wind.  An
absorption-line analysis that ignores these effects
would (i) systematically underestimate the true optical
depth and (ii) falsely conclude that the wind partially covers the
source.  We will find that this
[behaviour] is a generic result, even for wind models that include
dust and are not fully isotropic.

@@

The fiducial model does not include gas associated with
the interstellar medium of the galaxy, i.e.\ material at $r \sim
0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
results related solely to a wind component.  The decision to ignore the ISM
was also motivated by the general absence of significant absorption at
$\mdv \approx 0 \mkms$ in galaxies that exhibit outflows 
\citep[e.g.][]{wcp+09,rubin09,steidel+10}.
On the other hand, the stars that comprise the
source are very likely embedded within and fueled by gas
of the ISM.  
Consider, then, a modification to the fiducial model that 
includes an ISM. 
Specifically, we assume the ISM component has density $n_{\rm H} = 1 \cm{-3}$ for
$r_{\rm ISM} \le r < r_{\rm inner}$ with $r_{\rm ISM} = 0.5$\,kpc, 
an average velocity of $\mvr = 0 \mkms$, and a larger turbulent velocity $b_{\rm ISM} = 40 \mkms$.
%Figure~\ref{fig:ISM} summarizes the model.
The resultant optical depth profile $\tau_{2796}$ is identical to the
fiducial model for $r > 2$\,kpc, has a slightly higher opacity at
$r=1-2$\,kpc, and has a very large opacity at $r = 0.5-1$\,kpc.

@@

There are, however, several qualitative differences 
for the \ion{Fe}{2} transitions. 
First, the \feiia\ transition in the ISM+wind model
shows much stronger absorption at $\mdv \approx 0$
to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
the profile is not filled in by scattered photons. Instead, 
the majority of \feiia\ photons that are absorbed are re-emitted as
\feiis\~$\lambda\lambda 2612, 2632$ photons.  In fact, the
\feiia\ profile very nearly matches the profile without re-emission 
(compare to the dotted lines); this transition provides a
very good description of the intrinsic ISM+wind optical depth profile.  
We conclude that resonant transitions that are coupled to (multiple)
non-resonant, electric dipole transitions offer the best
diagnosis of ISM absorption.

@@

We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
using the 1D algorithm with no dust extinction; these are shown as
red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
should focus on the \mgiia\ transition.  The dotted line in the Figure
shows the intensity profile when one ignores re-emission
of absorbed photons.  By construction, it is the exact profile\footnote{Note that
  one should not make this comparison for the other transitions in
  the Sobolev model because those are scaled down by $f\lambda$ and
  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} 
described by Equation~\ref{eqn:LBG_I} and plotted in
Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
red curve)
shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
due to scattered photons.
In this respect, our LBG-Sobolev model is an
inaccurate description of the observations. The model
also predicts significant emission in the \ion{Mg}{2} lines and several of
the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
has been observed for \ion{Si}{2}$^*$
transitions in LBGs \citep{prs+02,shapley03}, but
the \ion{Fe}{2}$^*$ transitions
modeled here lie in the near-IR and have not yet been investigated.
On the other hand, there have been no 
reported detections of significant line-emission related to low-ion resonance
transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
\citep{wcp+09,rubin09}.  
The principal result is that the scattering and re-emission of
absorbed photons significantly alters the predicted absorption profiles
for the inputted model.  This is, of course, an unavoidable
consequence of an isotropic, dust-free model with unit covering
fraction.

@@

We also caution that the \ion{C}{4} emission observed for LBGs
\citep[e.g.][]{cb58} may result from the galactic-scale outflow, not
only the expected stellar winds of massive stars.

@@

On the other hand,
there are many examples of galaxies where blue-shifted absorption is
detected yet the authors report no significant line emission.  This
includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
ULIRGS by \cite{mb10}, and the extreme \ion{Mg}{2} outflows identified
by \cite{tremonti}.  Similarly, there have been no reports of
resonance line-emission from low-ion transitions in the LBGs\footnote{\citet{pettini02}
  reported and analyzed \ion{C}{4} line-emission from the lensed LBG
  cb58, attributing this flux to stellar winds.  We caution, however,
  that the galactic-scale wind proposed to exist for cb58 should also
  have contributed to the \ion{C}{4} line-emission.}, and a subset of
$z \lesssim 1$ galaxies show no detectable \ion{Mg}{2} or \ion{Fe}{2}*
emission (Rubin et al., in prep). 
These non-detections appear to contradict a primary conclusion of 
this paper.   We are motivated, therefore, to
reassess several of the effects that can reduce the line-emission
and consider whether these could preclude its detection for many
star-forming galaxies.  [If MgII emission is 'common' for HII regions,
why don't we see it *always* when we see OII, Hbeta, etc? Is it
trapped and then extincted? Same for FeII*]

@@

There is another (more subtle) effect that in principle will
substantially reduce the observed line emission: slit-loss.  As
described in Figures~\ref{fig:fiducial_ifu_mgii} and
\ref{fig:ISM_ifu}, emission from the wind is spatially extended with
a non-zero surface brightness predicted at large radii. This implies 
a non-negligible luminosity emitted well beyond the galaxy.  
The majority of observations of star-forming galaxies to date have
been taken through a spectroscopic slit designed to cover
the brightest continuum regions of the galaxy. Slits with angular
extents of $1-1.5''$ subtend roughly $8-15$\,kpc for galaxies at $z>0.5$.
Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
less than half the wind.  The result will be reduced line emission,
even when compared to the galaxy continuum.

@@

The previous few paragraphs sound a cautionary and largely negative
perspective on the implications for absorption-line analysis of
galactic-scale outflows, in the presence of (expected) significant
line-emission.   While this does complicate [the analysis],
observations of the line emission alone offer new and unique
constraints on the charcteristics of the outflow.  And when coupled
with the absorption-line data, the two sets of constraints...
The most direct measure provided by the line emission is an estimate
of the size and morphology of the outflow \citep[e.g.][]{rubin_emiss}.  
Line emission is predicted to extend to radii where the Sobolev
optical depth exceeds a few tenths [is that right?].  The principle
challenge is to achieve sufficient sensitivity to detect the low
surface brightness emission.

@@

\input{Tables/table_atomic.tex}
\input{Tables/tab_fiducial.tex}
\input{Tables/tab_fiducial_ew.tex}
\input{Tables/tab_meas_models.tex}
\input{Tables/tab_plaw_parm.tex}
\input{Tables/tab_meas_plaws.tex}

\begin{figure}
\epsscale{0.95}
\plotone{Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labeled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black upward arrows
indicate the resonance-line transitions, i.e.\ those connected to the ground
state.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the \feiis\ transitions that are connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
2618,2631$) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considered in our analysis.
}
\label{fig:energy}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_nvtau_vs_r.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the fiducial
wind model (see Table~\ref{tab:fiducial} for details).
The density and velocity laws are simple $r^{-2}$ and $r^1$
power-laws.  The optical depth profile was calculated by summing
the opacity at small and discrete radial intervals in velocity space
and was then converted to radius with the velocity law.  One notes that
the wind is optically thick at the inner radius ($r_{\rm inner} =
1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
  outer} = 20$\,kpc).
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:fiducial_nvt}
\end{figure}

>>>>

\newcommand{\msun}{M_\odot}
\newcommand{\tpk}{$\tau_{\rm pk}$}
\newcommand{\mtpk}{\tau_{\rm pk}}
\newcommand{\mdv}{\delta v}
\newcommand{\ewabs}{$W_{\rm a}$}
\newcommand{\ewe}{$W_{\rm e}$}
\newcommand{\rtt}{$r_{\tau = 0.2}$}
\newcommand{\mrtt}{r_{\tau = 0.2}}
\newcommand{\bturb}{$b_{\rm turb}$}
\newcommand{\mbturb}{b_{\rm turb}}
\newcommand{\taud}{$\tau_{\rm dust}$}
\newcommand{\mtaud}{\tau_{\rm dust}}
\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\feiis}{\ion{Fe}{2}$*$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {\, {\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

Beyond $z \sim 0$, galactic outflows are 
revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
\ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
as a backlight, one observes gas that is predominantly
blue-shifted which indicates a flow toward
Earth and away from the galaxy.  These transitions are sensitive to
the cool (\ion{Mg}{2}; $T \sim 10^4$K) and warm (\ion{C}{4}; $T \sim
10^5$K) phases of the flow.  The incidence of cool gas outflows is
nearly universal in star-forming galaxies;  this includes systems at $z \sim 0$
which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
\citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rwk+10}, and
$z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97,shapley03}.

@@

Recent studies of $z \sim 1$ star-forming galaxies have revealed that
the cool gas often exhibits significant resonant-line emission (e.g.\
\ion{Mg}{2}) in
tandem with the nearly ubiquitous blue-shifted absorption
\citep{wcp+09,rwk+10}.  The resultant spectra resemble the P-Cygni
profile characteristic of stellar winds.
\cite{rubin+10c} have also detected line
emission from non-resonant \ion{Fe}{2}$^*$ transitions 
Their interpretation is that the emission is the result of photons
scattered off the wind into our sightline, analogous to P-Cygni.
\cite{rubin+10c} also observed spatially extended \ion{Mg}{2} emission
which they use to estimate the size of the outflow.  They infer that
the wind extends to at least 5\,kpc from the galaxy.  Line emission is
also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
A comprehensive analysis of the emission lines
related to galactic-scale outflows
(e.g.\ via deep integral-field-unit observations) may offer unique
diagnostics on the morphology and density of the outflow, eventually
setting tighter constraints on the energetics of the flow.

[Phillips first reported?]
Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
and Rubin et al.\ 2011 (in prep).
\cite{wcp+09}, who
studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
\ion{Mg}{2} emission in a small subset of the individual galaxy
spectra of their large sample.  These were excluded from the full
analysis on concerns that the emission was related to AGN activity.
The stacked spectra of the remaining galaxies, however, also indicated
\ion{Mg}{2} emisison, both directly and when the authors modeled and
`removed' the $v \approx 0\mkms$ absorption component.  Although the
authors suggested the emission could be related to back-scattered
light in the wind, they also allowed that it could be related to weak
AGN activity.   Very similar \ion{Mg}{2} emission was observed by
\cite{rwk+10} who repeated the analysis of \cite{wcp+09} on a set
of lower redshift galaxies. 
[Did Kate see FeII* emission in her stacks? If not, why not?]

@@

Focusing further on the \ion{Mg}{2} absorption, one notes that the profiles lie
well above zero intensity and have similar depth even though their $f\lambda$
values differ by a factor of two.  In standard absorption line
analysis, this is 
the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
saturated) which only partially covers the emitting source
\citep[e.g.][]{hammann+10}.  Our fiducial wind model, however, 
{\it entirely covers the source}; the apparent partial covering must
be related to a different effect.
Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
absorption profiles from Figure~\ref{fig:fiducial_1d} against an
artificial model where no absorbed photons are 
re-emitted.   As expected from the
$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), this
`intrinsic' model
produces a strong \mgiid\ doublet that absorbs all photons at
$\delta v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
  max}_{2796}) \approx 0$.
The true model, in contrast, has been `filled in' at $\delta v \approx -100
\mkms$ by photons scattered in the wind.  An
absorption-line analysis that ignores these effects
would (i) systematically underestimate the true optical
depth and (ii) falsely conclude that the wind partially covers the
source.  We will find that this
[behaviour] is a generic result, even for wind models that include
dust and are not fully isotropic.

@@

The fiducial model does not include gas associated with
the interstellar medium of the galaxy, i.e.\ material at $r \sim
0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
results related solely to a wind component.  The decision to ignore the ISM
was also motivated by the general absence of significant absorption at
$\mdv \approx 0 \mkms$ in galaxies that exhibit outflows 
\citep[e.g.][]{wcp+09,rwk+10,steidel+10}.
On the other hand, the stars that comprise the
source are very likely embedded within and fueled by gas
of the ISM.  
Consider, then, a modification to the fiducial model that 
includes an ISM. 
Specifically, we assume the ISM component has density $n_{\rm H} = 1 \cm{-3}$ for
$r_{\rm ISM} \le r < r_{\rm inner}$ with $r_{\rm ISM} = 0.5$\,kpc, 
an average velocity of $\mvr = 0 \mkms$, and a larger turbulent velocity $b_{\rm ISM} = 40 \mkms$.
%Figure~\ref{fig:ISM} summarizes the model.
The resultant optical depth profile $\tau_{2796}$ is identical to the
fiducial model for $r > 2$\,kpc, has a slightly higher opacity at
$r=1-2$\,kpc, and has a very large opacity at $r = 0.5-1$\,kpc.

@@

There are, however, several qualitative differences 
for the \ion{Fe}{2} transitions. 
First, the \feiia\ transition in the ISM+wind model
shows much stronger absorption at $\mdv \approx 0$
to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
the profile is not filled in by scattered photons. Instead, 
the majority of \feiia\ photons that are absorbed are re-emitted as
\feiis$\lambda\lambda 2612, 2632$ photons.  In fact, the
\feiia\ profile very nearly matches the profile without re-emission 
(compare to the dotted lines); this transition provides a
very good description of the intrinsic ISM+wind optical depth profile.  
We conclude that resonant transitions that are coupled to (multiple)
non-resonant, electric dipole transitions offer the best
diagnosis of ISM absorption.

@@

We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
using the 1D algorithm with no dust extinction; these are shown as
red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
should focus on the \mgiia\ transition.  The dotted line in the Figure
shows the intensity profile when one ignores re-emission
of absorbed photons.  By construction, it is the exact profile\footnote{Note that
  one should not make this comparison for the other transitions in
  the Sobolev model because those are scaled down by $f\lambda$ and
  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} 
described by Equation~\ref{eqn:LBG_I} and plotted in
Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
red curve)
shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
due to scattered photons.
In this respect, our LBG-Sobolev model is an
inaccurate description of the observations. The model
also predicts significant emission in the \ion{Mg}{2} lines and several of
the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
has been observed for \ion{Si}{2}$^*$
transitions in LBGs \citep{prs+02,shapley03}, but
the \ion{Fe}{2}$^*$ transitions
modeled here lie in the near-IR and have not yet been investigated.
On the other hand, there have been no 
reported detections of significant line-emission related to low-ion resonance
transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
\citep{wcp+09,rwk+10}.  
The principal result is that the scattering and re-emission of
absorbed photons significantly alters the predicted absorption profiles
for the inputted model.  This is, of course, an unavoidable
consequence of an isotropic, dust-free model with unit covering
fraction.

@@

We also caution that the \ion{C}{4} emission observed for LBGs
\citep[e.g.][]{prs+02} may result from the galactic-scale outflow, not
only the expected stellar winds of massive stars.

@@

On the other hand,
there are many examples of galaxies where blue-shifted absorption is
detected yet the authors report no significant line emission.  This
includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
ULIRGS by \cite{mb09}, and the extreme \ion{Mg}{2} outflows identified
by \cite{tmd07}.  Similarly, there have been no reports of
resonance line-emission from low-ion transitions in the
LBGs\footnote{\citet{psa+00}
  reported and analyzed \ion{C}{4} line-emission from the lensed LBG
  cb58, attributing this flux to stellar winds.  We caution, however,
  that the galactic-scale wind proposed to exist for cb58 should also
  have contributed to the \ion{C}{4} line-emission.}, and a subset of
$z \lesssim 1$ galaxies show no detectable \ion{Mg}{2} or \ion{Fe}{2}*
emission (Rubin et al., in prep). 
These non-detections appear to contradict a primary conclusion of 
this paper.   We are motivated, therefore, to
reassess several of the effects that can reduce the line-emission
and consider whether these could preclude its detection for many
star-forming galaxies.  [If MgII emission is 'common' for HII regions,
why don't we see it *always* when we see OII, Hbeta, etc? Is it
trapped and then extincted? Same for FeII*]

@@

There is another (more subtle) effect that in principle will
substantially reduce the observed line emission: slit-loss.  As
described in Figure~\ref{fig:fiducial_ifu_mgii}, 
emission from the wind is spatially extended with
a non-zero surface brightness predicted at large radii. This implies 
a non-negligible luminosity emitted well beyond the galaxy.  
The majority of observations of star-forming galaxies to date have
been taken through a spectroscopic slit designed to cover
the brightest continuum regions of the galaxy. Slits with angular
extents of $1-1.5''$ subtend roughly $8-15$\,kpc for galaxies at $z>0.5$.
Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
less than half the wind.  The result will be reduced line emission,
even when compared to the galaxy continuum.

@@

The previous few paragraphs sound a cautionary and largely negative
perspective on the implications for absorption-line analysis of
galactic-scale outflows, in the presence of (expected) significant
line-emission.   While this does complicate [the analysis],
observations of the line emission alone offer new and unique
constraints on the charcteristics of the outflow.  And when coupled
with the absorption-line data, the two sets of constraints...
The most direct measure provided by the line emission is an estimate
of the size and morphology of the outflow \citep[e.g.][]{rubin+10c}.  
Line emission is predicted to extend to radii where the Sobolev
optical depth exceeds a few tenths [is that right?].  The principle
challenge is to achieve sufficient sensitivity to detect the low
surface brightness emission.

@@

\input{../Tables/table_atomic.tex}
\input{../Tables/tab_fiducial.tex}
\input{../Tables/tab_fiducial_ew.tex}
\input{../Tables/tab_meas_models.tex}
\input{../Tables/tab_plaw_parm.tex}
\input{../Tables/tab_meas_plaws.tex}

\begin{figure}
\epsscale{0.95}
\plotone{../Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labeled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black upward arrows
indicate the resonance-line transitions, i.e.\ those connected to the ground
state.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the \feiis\ transitions that are connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
2618,2631$) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considered in our analysis.
}
\label{fig:energy}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{../Figures/fig_nvtau_vs_r.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the fiducial
wind model (see Table~\ref{tab:fiducial} for details).
The density and velocity laws are simple $r^{-2}$ and $r^1$
power-laws.  The optical depth profile was calculated by summing
the opacity at small and discrete radial intervals in velocity space
and was then converted to radius with the velocity law.  One notes that
the wind is optically thick at the inner radius ($r_{\rm inner} =
1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
  outer} = 20$\,kpc).
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:fiducial_nvt}
\end{figure}
